Missing data: Current practice in football research and recommendations for reporting missingness

### 2020-09-02 paper/paper.Rmd
first pass at addressing #3

Missing data can undermine the validity and accuracy of research results
[@Sainani2015; @Nakagawa2008; @Sterne2009]. Data can go
missing many ways. For example, accidentally skipping a survey question,
equipment failure, or intentionally not recording values. Before
analysis, missing data must be handled, with values typically deleted or
imputed. There is no universal approach to handling missing data. 
Contextual factors--such as, the study design and objective, and
pattern of missingness--determine how to handle missings on a
case-by-case basis [@Sainani2015].
The effect of missing data on the validity and accuracy of a study's
results is largely determined by the reasons for missingness, and how
missing data are handled.

>>>>

Missing data are values that should have been observed, but were not. Since the
values are unobserved, this can mean the population of interest might not be 
properly sampled, inducing bias into study results. Left undetected or poorly handled, missing data can undermine the validity and accuracy of research results
[@Sainani2015; @Nakagawa2008; @Sterne2009]. Data can go
missing many ways. For example, accidentally skipping a survey question,
equipment failure, or intentionally not recording values. Before
analysis, missing data must be handled, with values typically deleted or
imputed. There is no universal approach to handling missing data. 
Contextual factors--such as, the study design and objective, and
pattern of missingness--determine how to handle missings on a
case-by-case basis [@Sainani2015].
The effect of missing data on the validity and accuracy of a study's
results is largely determined by the reasons for missingness, and how
missing data are handled.

For a value to be missing, it should have been observed in the data, but was not. For example, a goal scored in football takes place, but the scorekeeper wasn't paying attention and did not record an event. This "goal" is now a missing value. Compare this to a game being rained out and no game taking place. There is no data to be observed, so there is no missing data.
